Thermodynamic fragments in magic state theories

### 2020-12-14 magic_paper.tex
minor typos
Added mana bound. Started discussion on thermal fragment

\section{Magic in the unital fragment}\label{sec:unital}
The unital fragment encompasses the circuits which preserve the maximally mixed state ($\id/d$) and so it includes many important families of circuits.

@@

\subsection{Distillation rate bounds for the unital fragment}\label{sec:lcsu}

@@

Here we focus on the case of Lorenz curves of even copies $\nn, \tt$ and low noise levels ($\epsilon \leq 3/7$).
The part of the curve on the LHS of its peak is constructed by the positive components of the state Wigner distribution that take values $w_\ii$, with associated multiplicities $\mlt_\ii$,
\begin{align}
	w_\ii &= \left( \frac{1}{6} - \frac{1}{18}\epsilon \right)^{2\ii}\left( -\frac{1}{3} + \frac{4}{9}\epsilon \right)^{\nn-2\ii}, \\
	m_\ii &= 8^{2\ii}\binom{\nn}{2\ii},
\end{align}
where $i=0,\dots,\frac{n}{2}$.
From this, it is readily seen that $\lc{\rho}{\id/3}(x)$ has elbows on the LHS of its peak located at points $x=x_\ii$, where
\begin{equation}
	x_\ii = \Phi_+ \left( 2\ii, \nn , \frac{8}{9} \right),
\end{equation}
with $\ii = 0,1, \dots , n$ and where $\Phi_+(i,n,p)$ is an even-power cumulant distribution function given by
\begin{equation}
	\Phi_+(2\ii, \nn, p) \coloneqq \sum_{\dummy=0}^{\ii} \binom{\nn}{2\dummy} p ^{2\dummy} (1-p)^{\nn-2\dummy}.
\end{equation}
We provide technical details on the function $\Phi_+$ in the appendices.

@@

The first elbow of the target state is located at $x'_0 = \frac{1}{9^{\tt}} > x_\star$, so in order to find the target state Lorenz curve coordinate $L'_\star$ at location $x_\star$, we can interpolate between the origin and the first target state elbow, 
\begin{equation}
	\begin{split}
	L'_\star &= \frac{x_\star}{x'_0}L'_0 = \frac{1}{9^{\nn-\tt}}\left( \frac{5}{3} - \frac{8}{9}\epsilon'\ \right)^{\tt}\Phi_+\left(0;\tt,\frac{12-4\epsilon'}{15-8\epsilon'}\right) \\
	&= \frac{(3-4\epsilon')^{\tt}}{9^{\nn}}.
	\end{split}
\end{equation}
The process in~\cref{eq:sudist} is therefore possible only if $L_\star \geq L'_\star$ or equivalently,
\begin{align}
	\frac{n'}{n} &\leq \frac{\ln{(3-4\epsilon)}}{\ln{(3-4\epsilon')}}, \\
	\epsilon &\leq \frac{3}{4} - \frac{1}{4}(3-4\epsilon')^{\frac{\tt}{\nn}}.
\end{align}
As an example, the process with $(\nn, \tt) = (12, 4)$ and $\epsilon' = 0.05$ yields $\epsilon \leq 0.398$.
Numerical comparison of the curves with varying $\epsilon$ suggests that we require $\epsilon \leq 0.373$ for the process to be possible.
\nick{All numerical examples I have tested, for various different cases, are quite close}

Moreover, for the problem of distilling pure magic states where $\epsilon'=0$ we obtain an upper bound on the unital fragment distillation rate $R=n/n'$ given by
\begin{equation}
R \le \frac{\ln (3-4 \epsilon)}{\ln 3},
\end{equation}
which holds for all finite $n$. In comparison, the bound from mana gives $ R \le $ \ddd{[GIVE VALUE]}.

\ddd{[This is good, and the bound coming from the first elbow seems very easy to obtain. Going forward:
\begin{enumerate}
\item Does the ``last elbow'' give the same bound? Is it as simple?
\item Numerically is this about as good as it gets from majorization?
\item How does this rate compare with existing literature?
\end{enumerate}
If this bound is better than existing literature then great. I suspect not though. However, remember the core message of our work is that we're ``incorporating physical restrictions'' into the magic analysis. Given this, one thing that would round the paper off could be if we re-played the ``first elbow'' bound for some non-trivial temperature. Meaning: choose a ``nice'' Hamiltonian and compute the first elbow constraint via the thermo-majorization distortion of the Wigner components. This would then give us something clearly new -- namely a bound with temperature dependence! People would find this interesting since nothing like it exists yet.}
\null\newpage
\null\newpage

@@

>>>>

\section{Magic in unital and thermal fragments}\label{sec:unital}
The unital fragment encompasses the circuits which preserve the maximally mixed state ($\id/d$) and so it includes many important families of circuits.

@@

\subsection{Distillation rate bounds in the unital fragment}\label{sec:lcsu}

@@

Here we focus on the case of Lorenz curves of even copies $\nn, \tt$ and low noise levels ($\epsilon \leq 3/7$).
The part of the curve on the LHS of its peak is constructed by the positive components of the state Wigner distribution that take values $w_\ii$, with associated multiplicities $\mlt_\ii$,
\begin{align}
	w_\ii &= \left( \frac{1}{6} - \frac{1}{18}\epsilon \right)^{2\ii}\left( -\frac{1}{3} + \frac{4}{9}\epsilon \right)^{\nn-2\ii}, \\
	m_\ii &= 8^{2\ii}\binom{\nn}{2\ii},
\end{align}
where $i=0,\dots,\frac{n}{2}$.
From this, it is readily seen that $\lc{\rho}{\id/3}(x)$ has elbows on the LHS of its peak located at points $x=x_\ii$, where
\begin{equation}
	x_\ii = \Phi_+ \left( 2\ii; \nn , \frac{8}{9} \right),
\end{equation}
with $\ii = 0,1, \dots , n$ and where $\Phi_+(i,n,p)$ is an even-power cumulant distribution function given by
\begin{equation}
	\Phi_+(2\ii; \nn, p) \coloneqq \sum_{\dummy=0}^{\ii} \binom{\nn}{2\dummy} p ^{2\dummy} (1-p)^{\nn-2\dummy}.
\end{equation}
We provide technical details on the function $\Phi_+$ in the appendices.

@@

The first elbow of the target state is located at $x'_0 = \frac{1}{9^{\tt}} > x_\star$, so in order to find the target state Lorenz curve coordinate $L'_\star$ at location $x_\star$, we can interpolate between the origin and the first target state elbow, 
\begin{equation}
	\begin{split}
	L'_\star &= \frac{x_\star}{x'_0}L'_0 = \frac{1}{9^{\nn-\tt}}\left( \frac{5}{3} - \frac{8}{9}\epsilon'\ \right)^{\tt}\Phi_+\left(0;\tt,\frac{12-4\epsilon'}{15-8\epsilon'}\right) \\
	&= \frac{(3-4\epsilon')^{\tt}}{9^{\nn}}.
	\end{split}
\end{equation}
The process in~\cref{eq:sudist} is therefore possible only if $L_\star \geq L'_\star$ or equivalently,
\begin{align}
	\frac{n}{n'} &\geq \frac{\ln{(3-4\epsilon')}}{\ln{(3-4\epsilon)}}, \text{ or}\\
	\epsilon &\leq \frac{3}{4} - \frac{1}{4}(3-4\epsilon')^{\frac{\tt}{\nn}}.
\end{align}
As an example, the process with $(\nn, \tt) = (12, 4)$ and $\epsilon' = 0.05$ yields $\epsilon \leq 0.398$.
Numerical comparison of the curves with varying $\epsilon$ suggests that we require $\epsilon \leq 0.373$ for the process to be possible.

Moreover, for the problem of distilling pure magic states where $\epsilon'=0$ we obtain a \nick{lower} bound on the unital fragment distillation rate $R=n/n'$ given by
\begin{equation}
R \geq \frac{\ln (3-4 \epsilon)}{\ln 3},
\end{equation}
which holds for all finite $n$. 
In comparison, the bound from mana gives 
\begin{equation}
	R_{\rm{mana}} \geq \frac{\ln \left(\frac{5}{3} - \frac{8}{9}\epsilon \right)}{\ln \frac{5}{3}},
\end{equation}
a threshold which is lower/looser than the one provided by majorization for all $\epsilon > 0$.

\ddd{[This is good, and the bound coming from the first elbow seems very easy to obtain. Going forward:
\begin{enumerate}
\item Does the ``last elbow'' give the same bound? Is it as simple?
\item Numerically is this about as good as it gets from majorization?
\item How does this rate compare with existing literature?
\end{enumerate}
If this bound is better than existing literature then great. I suspect not though. However, remember the core message of our work is that we're ``incorporating physical restrictions'' into the magic analysis. Given this, one thing that would round the paper off could be if we re-played the ``first elbow'' bound for some non-trivial temperature. Meaning: choose a ``nice'' Hamiltonian and compute the first elbow constraint via the thermo-majorization distortion of the Wigner components. This would then give us something clearly new -- namely a bound with temperature dependence! People would find this interesting since nothing like it exists yet.}

@@

For a qutrit, let the energy spectrum be $E_0 \geq E_1 \geq E_2$. 
Then, we can explicitly write the thermal Wigner distribution as
\begin{equation}
	\W{\gamma_\beta} = \frac{1}{3\Z_\beta} \big( \overbrace{e^{-\beta E_0}}^3, \overbrace{e^{-\beta E_1}}^3, \overbrace{e^{-\beta E_2}}^3 \big),
\end{equation}
which is sorted in decreasing order.
We choose the Strange state where the negativity is in the first component of its Wigner distribution
\begin{equation}\label{eq:wsu}
	\W{\noisys(\epsilon)} = \Bigg( \overbrace{-\frac{1}{3} + \frac{4}{9}\epsilon}^1, \overbrace{\frac{1}{6} - \frac{1}{18}\epsilon}^8\Bigg),
\end{equation}

However, higher copies are not sorted, for example
\begin{equation}
	\begin{split}
	\W{\gamma_\beta\too{2}} = \frac{1}{9\Z_\beta^2} \Bigg( &\overbrace{\overbrace{e^{-\beta 2E_0}}^3, \overbrace{e^{-\beta (E_0 + E_1)}}^3, \overbrace{e^{-\beta (E_0 + E_2)}}^3}^3, \\
	 &\overbrace{\overbrace{e^{-\beta (E_1 + E_0)}}^3, \overbrace{e^{-\beta 2E_1}}^3, \overbrace{e^{-\beta (E_1 + E_2)}}^3}^3, \\
	 &\overbrace{\overbrace{e^{-\beta (E_2 + E_0)}}^3, \overbrace{e^{-\beta (E_2 + E_1)}}^3, \overbrace{e^{-\beta 2E_2}}^3}^3 \Bigg).
	\end{split}
\end{equation}
For the Strange state we have
\begin{equation}
	\begin{split}
	\W{\noisys(\epsilon)\too{2}} = \Bigg( &\overbrace{\left( -\frac{1}{3} + \frac{4}{9}\epsilon \right)^2}^1, \overbrace{ \left( -\frac{1}{3} + \frac{4}{9}\epsilon \right) \left( \frac{1}{6} - \frac{1}{18}\epsilon \right)}^{8}, \\
	&\overbrace{\overbrace{ \left( -\frac{1}{3} + \frac{4}{9}\epsilon \right) \left( \frac{1}{6} - \frac{1}{18}\epsilon \right)}^1, \overbrace{\left( \frac{1}{6} - \frac{1}{18}\epsilon \right)^2}^8}^8,  \Bigg).
	\end{split}
\end{equation}
\nick{We need to sort the distributions $\W{\gamma_\beta\too{2}}, \W{\noisys(\epsilon)\too{2}}$, so that the vector
\begin{equation}
	\tilde{\bm{w}} \coloneqq \left(\frac{(\W{\noisys(\epsilon)\too{2}})_1}{(\W{\sigma})_1}, \dots, \frac{(\W{\rho})_{81}}{(\W{\sigma})_{81}} \right)^T,
\end{equation}
is in decreasing order, i.e. $\tilde{\bm{w}} = \tilde{\bm{w}}^\downarrow$.
Then, we need to generalise for any number of copies $n$}

\null\newpage
\null\newpage
